### 2016-05-22 unsat/response_CP2016.txt

Review 1:
-- Originality issue?
Our heuristics are original, and proved to be effective by our experiments.

Review 2:
-- Any kind of theoretical guarantees?
No, because the procedure of computing a Groebner basis does not guarantee that we can deduce all polynomial dependences in the original set.
--  In your experiments the GB-core algorithm runs only once and the syzygy heuristic does not provide further improvements?
See above.
-- It would be interesting to see how using the syzygy heuristic compares to re-running GB-core?
Syzygy heuristic requires GB computation, which is inefficient. For example, single run of GB computation for 200 polynomials could be hours. So we use syzygy heuristic as complementation to re-running GB-core.

Review 3:
-- The paper addresses the problem of finding small unsatisfiable cores in the context of Boolean formulas presented in XNF? 
Not exactly. Both Groebner basis and unsatisfiable cores are concepts not limited to XNF,  so our approach can be applied to any decision problem formalized by polynomials over any field.
-- Benchmarks must have been translated in the opposite direction too, for use by picoMUS?
The size of MUS for benchmarks not translated from CNF is not obtained by using picoMUS. Instead, we first get a smaller core using our approach, then reduce it to minimal using exhaustive deletion-based techniques.
-- The result for GB-core without the post-processing?
Okay.
-- The result for subset-3 must be wrong, as it suggests the proposed method finds a core that is smaller than the optimal result?
No, the smaller core obtained by our approach is not a subset of the core from picoMUS.
-- Consider publishing all benchmarks used, including those that have been modified by adding redundant clauses. I assume StarExec is the right venue for this?
Okay. But not StarExec.
-- Page 14, mid: "translation to CNF" -> "translation from CNF"?
Correct.
-- (Important) Page 14 (mid) suggests that any scalability issues stem from translation to/from CNF, but in [12] those issues must have been overcome?
(Need further discussion) Reference [12] does not overcome the scalability issue for GB computation. In that paper, the author divided the whole set of clauses into lots of small subsets, and GB computation is operated on small sets. In our case, partitioning is not helpful for identifying smaller cores because UNSAT problem is related to a global property rather than local ones.

Review 4:
-- Is the refutation tree really helpful in the construction? Is it used for storing the computed polynomials in a more efficient way?
The refutation tree is a structure helpful in illustrating the resolution-style refutation when running the Buchberger's algorithm. We do not use a tree-like data structure to actually storing the data. We have introduced the data structure in section 4.2,  especially in Algorithm 2.
-- What is the criterion used to stop the refinement procedure (besides considering the size of the unsat core computed by another tool)?
We stop the refinement when the size of core do not decrease after more GB-core iterations are taken. It is a fixpoint detection mechanism that not rely on the MUS we learn in advance.
-- How do the execution times compare with those of picoMUS?
As the GB computation is hard and our tool is not well specialized,  the runtime is much larger than conventional tools -- their runtimes are usually less than 1 ms.
-- Is picoMUS the only solver to compare with? Why?
No,  we also compare the results from MUSer2 and HaifaMUC. They are identical for our benchmarks. We choose these 3 solvers because they have best performance on SAT 2011 competition,  which is the latest SAT competition with a MUS track.
(URL for HaifaMUC: http://ie.technion.ac.il/~ofers/haifasolvers/)

### 2016-05-24 unsat/response_CP2016.txt

Review 1:
-- Originality issue?
Our heuristics are original, and proved to be effective by our experiments.

Review 2:
-- Any kind of theoretical guarantees?
No. This is a hard theoretical problem in algebra, because a redundant polynomial can always be written as combination of necessary polynomials, while the procedure of computing a Groebner basis does not guarantee that we can deduce all polynomial dependences in the original set. The GB computation procedure can be controlled by both monomial order and strategy to pick critical s-poly pairs, which is infeasible for exhaustive method.
--  In your experiments the GB-core algorithm runs only once and the syzygy heuristic does not provide further improvements?
Although syzygy heuristic gather extra information from the GB computation, it is still not sufficient to derive all polynomial dependencies.
-- It would be interesting to see how using the syzygy heuristic compares to re-running GB-core?
Syzygy heuristic collects extra information from GB-core algorithm, so the number of rows of syzygy matrix will be much greater than the size of original polynomial set. Since it requires a full GB computation on each column of syzygy matrix, it will take too much time. For example, if we directly apply syzygy heuristic on aim-100 benchmark (79 polynomials), there are 426 rows in syzygy matrix, it is too large such that GB computation for a single column takes hours. So we use syzygy heuristic as complementation to re-running GB-core.

Review 3:
-- The paper addresses the problem of finding small unsatisfiable cores in the context of Boolean formulas presented in XNF? 
Not exactly. Both Groebner basis and unsatisfiable cores are concepts not limited to XNF,  so our approach can be applied to any decision problem formalized by polynomials over any field.
-- Benchmarks must have been translated in the opposite direction too, for use by picoMUS?
The size of MUS for benchmarks not translated from CNF is not obtained by using picoMUS. Instead, we first get a smaller core using our approach, then reduce it to minimal using exhaustive deletion-based techniques.
-- The result for GB-core without the post-processing?
We have the data and will be happy to share with the PC.
-- The result for subset-3 must be wrong, as it suggests the proposed method finds a core that is smaller than the optimal result?
No, the smaller core obtained by our approach is not a subset of the core from picoMUS. Actually we obtained a different minimal core using another MUS extractor (HaifaMUC).
-- Consider publishing all benchmarks used, including those that have been modified by adding redundant clauses. I assume StarExec is the right venue for this?
We would love to share our benchmarks and tool with the PC and the public.
-- Page 14, mid: "translation to CNF" -> "translation from CNF"?
We accept this suggestion.
-- (Important) Page 14 (mid) suggests that any scalability issues stem from translation to/from CNF, but in [12] those issues must have been overcome?
Reference [12] does not overcome the scalability issue for GB computation. In that paper, the author divided the whole set of clauses into lots of small subsets, and GB computation is operated on small sets. In our case, partitioning is not helpful for identifying smaller cores because UNSAT problem is related to a global property rather than local ones.

Review 4:
-- Is the refutation tree really helpful in the construction? Is it used for storing the computed polynomials in a more efficient way?
The refutation tree is a structure helpful in illustrating the resolution-style refutation when running the Buchberger's algorithm, as well as introducing concepts such as refutation distance and frequency of occurence. We do not use a tree-like data structure to actually storing the data. In Algorithm 2, data set D is necessary, while the construction of refutation tree T is optional and it has similar cost with extracting distance and frequency from D.
-- What is the criterion used to stop the refinement procedure (besides considering the size of the unsat core computed by another tool)?
We stop the refinement when the size of core do not decrease after more GB-core iterations are taken. It is a fixpoint detection mechanism that not rely on the MUS we learn in advance.
-- How do the execution times compare with those of picoMUS?
As the GB computation is hard and our tool is implemented through Singular which is a universal symbolic computing system that not well specialized,  the runtime is much larger than conventional tools -- their runtimes are usually less than 0.1 sec.
-- Is picoMUS the only solver to compare with? Why?
No,  we also compare the results from MUSer2 and HaifaMUC and they show identical results for most of our benchmarks. For several benchmarks (subset1~3, phole4) they give different solutions, the results from picoMUS are usually the same or a subset of the output from our tool (for subset3 our result is better than all other ones). We choose these 3 solvers because they have best performance on SAT 2011 competition (ranking 1,2,4,5 on number of solved instances and 1,2,3,5 on average CPU time for solving single instance),  which is the latest SAT competition with a MUS track.
(word count: 865)

### 2016-09-25 dissertation/normal.tex
dissertation -- NB part 1

\chapter{Functional Verification of Sequential Normal Basis Multiplier}
\label{ch:normal}
In order to utilize our traversal algorithm, it is necessary to find out
a sort of suitable circuit benchmarks which is easy to compute its
Gr\"bner basis (GB). From the work of Lv et al. \cite{lv_dissertation},
we learn that arithmetic circuits in Galois field (GF) is
convertible to an ideal of circuit polynomials, and the 
ideal generators form a GB itself with reverse topological
term order. Furthermore, according to the work of Pruss et al.
\cite{tim_dissertation}, with a limited computation complexity,
we can abstract the word-level signature of an arithmetic 
component working in GF. Thus, we consider the possibility 
of applying our traversal algorithm on sequential Galois
field circuits. In each frame, we can use the techniques 
from \cite{tim_dissertation} to abstract the word-level
signature of the combinational logic, which corresponds
to the transition function in our traversal algorithm.
As a result, we manage to find a type of sequential GF multiplier
which we can apply our traversal algorithm to actually 
verify its functional correctness.

\section{Motivation}
\label{sec:normal_motiv}

>>>>

\chapter{Functional Verification of Sequential Normal Basis Multiplier}
\label{ch:normal}
In order to utilize our traversal algorithm, it is necessary to find out
a sort of suitable circuit benchmarks which is easy to compute its
Gr\"bner basis (GB). From the work of Lv et al. \cite{lv_dissertation},
we learn that arithmetic circuits in Galois field (GF) is
convertible to an ideal of circuit polynomials, and the 
ideal generators form a GB themselves when applying reverse topological
term order. Furthermore, according to the work of Pruss et al.
\cite{tim_dissertation}, with a limited computation complexity,
we can abstract the word-level signature of an arithmetic 
component working in GF. Thus, we consider the possibility 
of applying our traversal algorithm on sequential Galois
field circuits. In each frame, we can use the techniques 
from \cite{tim_dissertation} to abstract the word-level
signature of the combinational logic, which corresponds
to the transition function in our traversal algorithm.
As a result, we manage to find a type of sequential GF multiplier
which we can apply our traversal algorithm to actually 
verify its functional correctness.

\section{Motivation}
\label{sec:normal_motiv}
From the preliminaries (Chapter \ref{ch:prelim}) about FSMs, we learn that the
Moore machine does not rely on inputs for state transitions. 
As depicted in Figure \ref{fig:Moore}(a), a typical Moore machine implementation
consists of combinational logic component and register files, where
$r_0,\dots,r_k$ are present state (PS) variables 
standing for state inputs (SI), and $r_0',\dots,r_k'$ are next state (NS) variables standing for
state outputs (SO). Figure \ref{fig:Moore}(b) shows the state transition graph (STG) of 
a Moore machine with $k+1$ distinct states. We notice that it forms a simple chain,
with $k$ consecutive transitions the machine reaches final state $R_k$.

\begin{figure}[H]
\centering{
\includegraphics[width=3.5in]{newfig/Moore.eps}
\caption{A typical Moore machine and its state transition graph}
\label{fig:Moore}}
\end{figure}

In practice,
some arithmetic components are designed in sequential circuits similar to the structure in 
Figure \ref{fig:Moore}(a). Initially the operands are loaded into the registers, 
then the closed circuit executes without taking any additional information from outside,
and store the results in registers after $k$ clock cycles. Its behavior can be described using
STG in Figure \ref{fig:Moore}(b): state $R$ denotes the bits stored in registers. Concretely, $R_init$ is the initial
state (usually reset to all zeros), $R_1$ to $R_{k-1}$ are intermediate results stored as SO of current state and SI
for next state, and $R_k$ (or $R_{final}$) is the final result given by arithmetic circuits (and equals to the answer
to arithmetic function when circuit is working functional correctly).
This kind of design results in 
reusing a smaller combinational logic component such that the area cost is greatly optimized.
However, it also brings difficulties in verifying the the circuit functions.

\begin{figure}[H]
\centering{
\includegraphics[width=3.5in]{newfig/convention.eps}
\caption{Conventional verification techniques based on bit-level unrolling and equivalence checking}
\label{fig:convention}}
\end{figure}

Conventional methods to such a sequential circuit may consist of unrolling the circuit for 
$k$ time-frames, and performing an equivalence checking between the unrolled machine and
the specification function. However, the number of gates will grow fast when doing unrolling
on bit-level. Meanwhile the structural similarity based equivalence checking techniques 
will fail when the sequential circuit is highly customized and optimized from the naive specification 
function. As a result, conventional techniques is grossly inefficient for large circuits.
Therefore, a new method based on our proposed word-level FSM traversal technique is worthy to be explored.

\section{Galois Field multiplier and Normal Basis}
\subsection{Multiplier in Galois Field}

\subsection{Introduction to Normal Basis}
